---
title: "General Linear Model - Specific Designs"
author: "Lieven Clement"
date: "statOmics, Ghent University (https://statomics.github.io)"
format:
  html:
    toc: true
    number-sections: true
    theme: cosmo
    highlight-style: tango
    code-tools: true
    embed-resources: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE, comment = NA, echo = TRUE,
                      message = FALSE, warning = FALSE)
library(tidyverse)
```

# Introduction

In this section we will illustrate how specific designs, e.g. 

- two-way anova designs
- block designs 

can be analysed using the general linear model. 

# Two-way anova 

## Data 


48 rats were allocated to 

- 3 poisons (I,II,III) and 
- 4 treatments (A,B,C,D). 

```{r}
library(faraway)
data(rats)

library(GGally)
rats %>%
  ggpairs()
```


We have a design with a continuous response time (survival) and two factors: 

- Poison: I, II, III
- Treatment: A, B, C, D

The data exploration indicates that there seems to be an effect of both treatment and poison. 


